Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-01 PandaOverview.tex
Address Danila's and Ruslan's comments

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figures/panda_architecture.pdf}
  \end{center}
    \caption{PanDA architecture with the subsystems and components
    relevant to the integration of PanDA with supercomputers. Numbers indicates
    the execution process based on JEDI: From the submission of tasks (1) to the
    retrieval of their output (20). The monitoring subsystem, the architectural
    details of PanDA Pilot and the communication among subsystem's components
    are abstracted to improve clarity.}
\label{fig:architecture}
\end{figure}

@@

The relation between tasks and jobs can be one-to-one or one-to-many, and the
conversion between the two can by static or dynamic. During the LHC Run 1, PanDA
required users or applications to perform a static conversion between tasks and
jobs: tasks were described as a set of jobs with a fixed number of events and
then submitted to the PanDA Server.

@@

Once submitted to the PanDA Server, jobs are stored by the Task Buffer component
into a global queue implemented as a  database (Fig.~\ref{fig:architecture}:5).
When jobs are submitted directly to the PanDA Server, the Brokerage component is
used to bind jobs to available sites, depending on static information about the
resources available for each site. Jobs submitted by JEDI are already bound to
sites so no further brokerage is needed. Once jobs are bound to sites, the
Brokerage module communicates to the Data Service module what data sets need to
be made available on what site (Fig.~\ref{fig:architecture}:6). The Data Service
communicates these requirements to the ATLAS DDM (Fig.~\ref{fig:architecture}:7)
that, when needed, takes care of aggregating files into datasets and containers,
replicating them on the required sites (Fig.~\ref{fig:architecture}:8).

The AutoPyFactory subsystem communicates with the Task Buffer component of the
PanDA Server, acquiring information about jobs that are ready for execution on
specific (type of) sites (Fig.~\ref{fig:architecture}:9). On the basis of this
information, AutoPyFactory defines a set of suitable PanDA Pilots and
concurrently submits them to a Condor-G broker (Fig.~\ref{fig:architecture}:10).
This broker submits these pilots wrapped as jobs or VMs to the required sites
(Fig.~\ref{fig:architecture}:11).

@@

When a PanDA Pilot becomes available on a site, it
% bootstrap, download their code, collect information about the execution
% environment and
calls the Job Dispatcher module of the PanDA Server, requesting for a job to
execute (Fig.~\ref{fig:architecture}:12). The Job Dispatcher communicates with
the Task Buffer, requesting for a job that is bound to the site of that pilot
and ready to be executed. Task Buffer checks the global queue (i.e., the PanDA
database) and if such a job is available, it passes the job handler to the Job
Dispatcher. The Job Dispatcher dispatches the job to the PanDA Pilot
(Fig.~\ref{fig:architecture}:13).

@@

Upon receiving a job, a PanDA Pilot starts a monitoring process and forks a
subprocess for the execution of the job's payload. The job is setup, input data
are transferred from the designated staging in location
(Fig.~\ref{fig:architecture}:14), and the job's payload is executed
(Fig.~\ref{fig:architecture}:15). Once completed, output is transferred to the
staging out location (Fig.~\ref{fig:architecture}:16).

@@

The Data Service module of the PanDA Server tracks and collects the output
generated by each job (Fig.~\ref{fig:architecture}:17), updating jobs'
attributes via the Task Buffer module (Fig.~\ref{fig:architecture}:18). When the
output of all the jobs of a task are retrieved, it is made available to the user
via PanDA Server. When a task is submitted to JEDI, task is marked as done
(Fig.~\ref{fig:architecture}:19) and the result of its execution is made
available to the user by JEDI (Fig.~\ref{fig:architecture}:20).

>>>>

\mtnote{From Danila: DDM enacts decisions about registering files into datasets.
These decisions are made by productions. DDM DOES OT DECIDE which file should be
in which dataset.}\mtnote{Done.}
\mtnote{No communication between APF and PanDA Server (deleted arrow, adjust
numbers and related text)}\mtnote{Done.}
\mtnote{No more DDM Service on Edge on grid sites. DDM directly interacts with
SE (deleted arrows, moved number 8. Update labels and related text)}\mtnote{Done.}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figures/panda_architecture.pdf}
  \end{center}
    \caption{PanDA architecture with the subsystems and components
    relevant to the integration of PanDA with supercomputers. Numbers indicates
    the execution process based on JEDI: From the submission of tasks (1) to the
    retrieval of their output (19). The monitoring subsystem, the architectural
    details of PanDA Pilot and the communication among subsystem's components
    are abstracted to improve clarity.}
\label{fig:architecture}
\end{figure}

@@

The relation between tasks and jobs can be one-to-one or one-to-many, and the
conversion between the two can by static or dynamic. During the LHC Run 1, PanDA
required users or applications to perform a static conversion between tasks and
jobs: tasks were described as a set of jobs
% with a fixed number of events
and then submitted to the PanDA Server.

@@

Once submitted to the PanDA Server, jobs are stored by the Task Buffer component
into a global queue implemented as a  database (Fig.~\ref{fig:architecture}:5).
When jobs are submitted directly to the PanDA Server, the Brokerage component is
used to bind jobs to available sites, depending on static information about the
resources available for each site. Jobs submitted by JEDI are already bound to
sites so no further brokerage is needed.

Once jobs are bound to sites, the Brokerage module communicates to the Data
Service module what data sets need to be made available on what site
(Fig.~\ref{fig:architecture}:6). The Data Service communicates these
requirements to the ATLAS DDM (Fig.~\ref{fig:architecture}:7) that, when needed,
takes care of % aggregating files into datasets and containers,
replicating them on the required sites (Fig.~\ref{fig:architecture}:8).

% AutoPyFactory subsystem communicates with the Task Buffer component of the
% PanDA Server, acquiring information about jobs that are ready for execution on
% specific (type of) sites (Fig.~\ref{fig:architecture}:9). On the basis of this
% information,
Meanwhile, AutoPyFactory defines a set of suitable PanDA Pilots and concurrently
submits them to a Condor-G broker (Fig.~\ref{fig:architecture}:9). This broker
submits these pilots wrapped as jobs or VMs to the required sites
(Fig.~\ref{fig:architecture}:10).

@@

When a PanDA Pilot becomes available on a site, it calls the Job Dispatcher
module of the PanDA Server, requesting for a job to execute
(Fig.~\ref{fig:architecture}:11). The Job Dispatcher interrogates the Task
Buffer module for a job that is bound to the site of that pilot and ready to be
executed. Task Buffer checks the global queue (i.e., the PanDA database) and,
upon availability, returns a suitable job the Job Dispatcher. The Job Dispatcher
dispatches that job to the PanDA Pilot (Fig.~\ref{fig:architecture}:12).

@@

Upon receiving a job, a PanDA Pilot starts a monitoring process and forks a
subprocess for the execution of the job's payload. The job is set up, input data
are transferred from the designated staging-in location
(Fig.~\ref{fig:architecture}:13), and the job's payload is executed
(Fig.~\ref{fig:architecture}:14). Once completed, output is transferred to the
staging-out location (Fig.~\ref{fig:architecture}:15).

@@

The Data Service module of the PanDA Server tracks and collects the output
generated by each job (Fig.~\ref{fig:architecture}:16), updating jobs'
attributes via the Task Buffer module (Fig.~\ref{fig:architecture}:17). When the
output of all the jobs of a task are retrieved, it is made available to the user
via PanDA Server. When a task is submitted to JEDI, task is instead marked as
done (Fig.~\ref{fig:architecture}:18) and the result of its execution is made
available to the user by JEDI (Fig.~\ref{fig:architecture}:19).
